Fully Automatic Loop-free Program Synthesis by Bounded Model Checking

### 2013-10-08 paper/paper.tex
Changed synthesize -> synthesise

When the first-order fragment of the logic is efficiently decidable and $P$ can be
expressed as a ground term of the logic, we can use a refinement loop to check the
validity of the synthesis formula as shown in Fig.~\ref{fig:abstract-refinement} and
Fig.~\ref{fig:abstract-refinement-code}.  The algorithm is divided into two
components: {\sc synth} and {\sc verif}.  We track a finite (small) set of inputs
and {\sc synth} synthesizes a candidate program that is correct on just those inputs.
{\sc Verif} then tries to verify the candidate program by searching for an input on
which the candidate program does not satisfy the specification.  If no such input
can be found, the candidate program is correct.  Otherwise, the new input is added
to the set of inputs we must check in {\sc synth}.  If the input set is finite, this
procedure is guaranteed to terminate.

@@

To synthesize tricky bitvector programs like this, it is natural for us to
work in the logic of quantifier-free propositional formulae and to use a
propositional SAT or SMT-$\mathcal{BV}$ solver as the decision procedure. 
However, we propose a slightly different tack, which is to use \newC as
our underlying logic.

@@

The only wrinkle here is that sometimes a program we synthesize will contain
constants.  If we have synthesized a program for a machine with $k$-bit words,
the constants in the program will be $k$ bits wide.  To generalize the program
to an $n$-bit machine (with $n > k$), we need some way of deriving $n$-bit-wide
numbers from $k$-bit ones.  We have several strategies for this and
just try each in turn.  In the following, a subscript $n$ on a value means that
the value is an $n$-bit word.  The dot operator $a_l \cdot b_m$ denotes
concatenation, resulting in an $(l+m)$-bit wide word.  A superscript on a value
means duplication, so $a_l^m$ means concatenating together $m$ copies of the $l$-bit
word $a$, resulting in an $(lm)$-bit wide word.

@@

As with program length we can progressively increase the number of constants in
our program.  We start by trying to synthesize a program with no constants, then
if that fails we try to synthesize using one constant and so on.

>>>>

When the first-order fragment of the logic is efficiently decidable and $P$ can be
expressed as a ground term of the logic, we can use a refinement loop to check the
validity of the synthesis formula as shown in Fig.~\ref{fig:abstract-refinement} and
Fig.~\ref{fig:abstract-refinement-code}.  The algorithm is divided into two
components: {\sc synth} and {\sc verif}.  We track a finite (small) set of inputs
and {\sc synth} synthesises a candidate program that is correct on just those inputs.
{\sc Verif} then tries to verify the candidate program by searching for an input on
which the candidate program does not satisfy the specification.  If no such input
can be found, the candidate program is correct.  Otherwise, the new input is added
to the set of inputs we must check in {\sc synth}.  If the input set is finite, this
procedure is guaranteed to terminate.

@@

To synthesise tricky bitvector programs like this, it is natural for us to
work in the logic of quantifier-free propositional formulae and to use a
propositional SAT or SMT-$\mathcal{BV}$ solver as the decision procedure. 
However, we propose a slightly different tack, which is to use \newC as
our underlying logic.

@@

The only wrinkle here is that we will sometimes synthesise a program containing
constants.  If we have synthesised a program for a machine with $k$-bit words,
the constants in the program will be $k$ bits wide.  To generalize the program
to an $n$-bit machine (with $n > k$), we need some way of deriving $n$-bit-wide
numbers from $k$-bit ones.  We have several strategies for this and
just try each in turn.  In the following, a subscript $n$ on a value means that
the value is an $n$-bit word.  The dot operator $a_l \cdot b_m$ denotes
concatenation, resulting in an $(l+m)$-bit wide word.  A superscript on a value
means duplication, so $a_l^m$ means concatenating together $m$ copies of the $l$-bit
word $a$, resulting in an $(lm)$-bit wide word.

@@

As with program length we can progressively increase the number of constants in
our program.  We start by trying to synthesise a program with no constants, then
if that fails we try to synthesise using one constant and so on.
